\documentclass{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tcolorbox}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{float}
\usepackage{xargs}
\usepackage{listofitems}

\setmainfont[Mapping=tex-text, BoldFont=Kabel_Bold.ttf]{Kabel_Regular.ttf}

\begin{document}
\input{cardCommands}

%
% FIA - chance, more likely to move the player
%
\begin{minipage}[!t][30cm][t]{9.89cm}
    \monChanceCard{FIA}{If you don't have the balls to brake late, that's your problem}{Advance to "Go".}
    \monChanceCard{FIA}{Tu-tu-du-du, Max Verstappen}{Advance to Netherlands. If you pass Go, collect \$200.}
    \monChanceCard{FIA}{It's *inhales* FORMULA 1 MSC CRUISES GRAN PREMIO DEL MADE IN ITALY E DELL'EMILIA-ROMAGNA time}{Advance to Imola. If you pass Go, collect \$200. }
    \monChanceCard{FIA}{Check the radio volume. Did you get that? DO YOU CHECK THE RADIO VOLUME?}{Advance token to the nearest Utility. If unowned, you may buy it from the Bank. If owned, throw dice and pay owner a total 10 times the amount thrown. }
    \monChanceCard{FIA}{You've got a problem, change your fucking car. - Then you change your car, because Checo has been saying the car is fucked.}{Advance to the nearest Development Department. If unowned, you may buy it from the Bank. If owned, pay owner twice the rent to which they are otherwise entitled.}
\end{minipage}
\begin{minipage}[!t][30cm][t]{9.89cm}
    \monChanceCard{FIA}{Anything can happen in F1, and it usually does.}{Bank pays you dividend of \$50.}
    \monChanceCard{FIA}{I understand that, without my agreement, the stewards have put out a press release late this afternoon that they summoned me. This is wrong and I have not been summoned by the stewards. I will not be going to the stewards.}{Escape the Stewards card. This card may be kept until needed, or traded/sold. }
    \monChanceCard{FIA}{Blue Flags, Michael. Blue Flags. This guy makes us lose the position.}{Go Back Three 3 Spaces.}
    \monChanceCard{FIA}{Nothing, just an inchident.}{Go directly to the stewards. Do not pass GO, do not collect \$200. }
    \monChanceCard{FIA}{To prevent manhole-covers from destroying any more underfloors, you need to inspect your circuits.}{Make general repairs on all your property: For each motorhome pay \$25, For each grandstand {pay} \$100.}
\end{minipage}
\begin{minipage}[!t][30cm][t]{9.89cm}
    \monChanceCard{FIA}{I'm losing power. I'm losing power. It's broken.}{Take a trip to the Powertrain Department. If you pass Go, collect \$200.}
    \monChanceCard{FIA}{Maybe don't touch the rear wing next time ...}{Pay Fine of \$15}
    \monChanceCard{FIA}{Gentlemen, a short view back to the past...}{Take a walk in Abu Dhabi. Advance token to Abu Dhabi}
    \monChanceCard{FIA}{Well, that's unfortunate.}{ Pay each player \$50.}
    \monChanceCard{FIA}{Your Dad owns the racing team.}{Receive \$150.}
\end{minipage}
\end{document}