\documentclass{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tcolorbox}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{float}
\usepackage{xargs}
\usepackage{listofitems}

\setmainfont[Mapping=tex-text, BoldFont=Kabel_Bold.ttf]{Kabel_Regular.ttf}

\begin{document}
\input{cardCommands}

%
% team radio - comm chest, more likely to give money
%
\begin{minipage}[!t][30cm][t]{9.89cm}
    \monChanceCard{Team Radio}{Multi 21}{You get 150 in prize money but you have to give 100 to any player.}
    \monChanceCard{Team Radio}{No Michael, No}{Go to the stewards, if you go over the grid, don't collect \$200}
    \monChanceCard{Team Radio}{Car feels good, much slower than before}{On your next turn only use one dice.}
    \monChanceCard{Team Radio}{This is a true Ferrari Strategy}{Advance to the Pirelli Factory}
    \monChanceCard{Team Radio}{"You came like a torpedo" - "I was racing"}{Advance to the next field a player stands on}
\end{minipage}
\begin{minipage}[!t][30cm][t]{9.89cm}
    \monChanceCard{Team Radio}{"IF YOU NO LONGER GO FOR A GAP THAT EXISTS, YOU’RE NO LONGER A RACING DRIVER."}{Advance to "Go". (Collect \$200)}
    \monChanceCard{Team Radio}{"SOMETIMES YOU’VE JUST GOT TO LICK THE STAMP AND SEND IT."}{From sale of stock you get \$50.}
    \monChanceCard{Team Radio}{"It's hammer time"}{Escape the Stewards card. - This card may be kept until needed or sold.}
    \monChanceCard{Team Radio}{"I should get move of the year, personality of the year... fair play maybe not"}{Bank error in your favor. Collect \$200.}
    \monChanceCard{Team Radio}{"MEIN GOTT! Muss das so sein?"}{Doctor's fees. Pay \$50.}
\end{minipage}
\begin{minipage}[!t][30cm][t]{9.89cm}
    \monChanceCard{Team Radio}{"Give me my gloves. My Gloves... MY GLOVES"}{You have won second prize in a beauty contest. Collect \$10.}
    \monChanceCard{Team Radio}{"I'm heavier than a freaking boat. Guys you need to build me a new car"}{You inherit \$100.}
    \monChanceCard{Team Radio}{Valteri, it's James. - James it's Valteri. Fuck you.}{Go directly to the stewards. Do not pass Go, Do not collect \$200.}
    \monChanceCard{Team Radio}{Box now. Box for hards. STAY OUT! STAY OUT! STAY OUT! \\-\\ Fuck fuck fuck. WHYYY?}{School fees. Pay \$50.}
    \monChanceCard{Team Radio}{You will not have the drink. We forgot to connect. You will not have the drink.}{It is your birthday. Collect \$10 from every player.}
\end{minipage}
\end{document}